Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-24 Methods-and-Results.Rmd
results structure added
intergroup contact added

histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)

```

@@

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}” (`r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses).

@@

>>>>

histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)
histogram(dtWorkerSupp$workerAvFreQual$PercContactNL)

histogram(dtWorkerSupp$workerAvFreQual$WinSumContactNL)

dtWorkerSupp$workerAvFreQual$WinSumContactNL %>% max

DescTools::Winsorize(dtWorkerSupp$workerAvFreQual$PercContactNL)

dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)

# misty::multilevel.descript(dtWorkerSupp$workerAvFreQual$SumContactNL, cluster = dtWorkerSupp$workerAvFreQual$ExternalReference)
```

@@

\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}”. Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
(`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; $N_{total}$ = `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts. These participants are removed from any analyses including outgroup contacts.}.

@@

\paragraph{Contact Hypothesis}

\paragraph{Core Need}

- Att ~ Need & Qlt ~ Need
- Att ~ Need + Qual

\paragraph{Robustness}

### 2021-10-24 Methods-and-Results.tex
intergroup contact added

To test the prerequisite effect of intergroup contact, every experience
sampling measurement started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
(31.59\% of all 1225 daily diary responses).

>>>>

To test the prerequisite effect of intergroup contact, every experience
sampling measurement started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
Our participants recorded between 2--51 (3.23--3.23\% of individual
daily diary measurements; \(N_{total}\) = 31.59\% of all 1225 daily
diary
responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts. These participants are removed from any analyses including outgroup contacts.}.
